### 2018-03-08 README.Rmd
Update md links in README

To see the things we are working on with the package as vignettes/Articles, check out 
the developmental `pkgdown` site at <https://infer-dev.netlify.com>.

@@

We welcome others helping us make this package as user friendly and efficient as possible. Please review
our [contributing](CONTRIBUTING.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
helping us to write `testthat` tests and help us in building vignettes that show how to (and how NOT to)
use the package.

>>>>

To see the things we are working on with the package as vignettes/Articles, check out 
the developmental `pkgdown` site at <http://bit.ly/infer-dev>.

@@

We welcome others helping us make this package as user friendly and efficient as possible. Please review
our [contributing](https://github.com/andrewpbray/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
helping us to write `testthat` tests and help us in building vignettes that show how to (and how NOT to)
use the package.
